\textbf{BibTrek Prototype: A Graph Visualization Tool and Search Engine for Cybersecurity Papers}

### 2019-07-29 article/article.tex
Added Acknowledgement section to the article

>>>>

\section{Acknowledgements}
The writer of this article would like to thank Professor Miguel L. Pardal and INESC-ID for having invited him for a one month summer-internship program. With this program the writer learned highly valuable knowledge in the areas of cybersecurity, distributed systems and scientific research from multiple researcher peers. Non only that but also acquired a greater  work from  and has the utmost gratitude for having been part of this project from which he has learned immensely from.
